---
title: "Standard Process for Rural Prefectures: Miyagi Prefecture as an Example"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Set Up and Data Cleaning Process
# 1.1 Set Up
```{r}
library(tidyverse)
set.seed(12345)

# pull functions from jcdf
# set working directory to the function folder
setwd("R")
files.sources = list.files()
sapply(files.sources, source)
# set working directory back to `jcdf`
setwd("..")
```

### Define Data on Prefecture
```{r}
sim_type <- "smc"
nsims <- 25000
pref_code <- 04
pref_name <- "miyagi"
lakes_removed <- c() 
ndists_new <- 5
ndists_old <- 6
```


# 1.2.Download and Clean Census Data
```{r}
# download census shapefile
pref_raw <- download_shp(pref_code)
dem_pops <- download_pop_demographics(pref_code)

# download 2020 census data
total <- download_2020_census(type = "total")
foreigner <- download_2020_census(type = "foreigner")
#Clean 2020 census
census2020 <- clean_2020_census(total = total, foreigner = foreigner)

# download historical boundary data
old_boundary <- download_old_shp(pref_code = pref_code)

# populations based on historical boundaries
pop_by_old_boundary <- download_2015pop_old(pref_code = pref_code)
```

## 1.3 Use clean_jcdf() function to clean census data
```{r}
pref <- pref_raw %>%
  clean_jcdf() %>%
  dplyr::group_by(code, CITY_NAME) %>%
  dplyr::summarise(geometry = sf::st_union(geometry)) %>%
  dplyr::left_join(census2020, by = c('code')) %>%
  dplyr::rename(pop = pop_national) %>%
  dplyr::select(code, pop, geometry)
```

### For Miyagi Prefecture only: reflect changes in municipality code
Tomiya-cho became Tomiya-shi in 2016. As we are dealing with census data both from 2015 and 2020, we must fix the municipality code of Tomiya-cho.
```{r}
# fix 富谷町 --> 富谷市 (2016 changes)
pref[which(pref$code == 4423), ]$pop <-  (census2020 %>% dplyr::filter(code == 4216, ))$pop_national
pref[which(pref$code == 4423), ]$code <- 4216
```

## 1.4 Use merge_gun() to make a new column for codes of guns
Miyagi-gun and Kurokawa-gun are split under the enacted plan. Thus, we allow those 2 guns to be split.
```{r}
pref <- merge_gun(pref, c(4401, 4421))
```

# 2. Run Simulations with 0 Municipality Splits
# 2.1 Finalize pref object
In this case, we merge together the gun and treat them as one geographical unit, except for the guns that are split under the status quo.
```{r}
pref_0 <- pref %>%
  dplyr::group_by(gun_code) %>%
  dplyr::summarize(geometry = sf::st_union(geometry),
                   pop = sum(pop),
                   code = gun_code[1])
```

# 2.2 Make adjacency graph
```{r}
prefadj_0 <- redist::redist.adjacency(pref_0)
```

# 2.3 Add edges to adjacency graph
In this case, there are no edges to add as there are no areas disconnected from the mainland.
```{r}
ferries_0 <- add_ferries(pref_0)
prefadj_0 <- geomander::add_edge(prefadj_0, ferries_0$V1, ferries_0$V2)
```

# 2.4 Define redist.map object
```{r}
pref_map_0 <- redist::redist_map(pref_0,
                                 ndists = ndists_new,
                                 pop_tol= 0.08,
                                 total_pop = pop,
                                 adj = prefadj_0)
```


#2.5 Run Simulation
```{r}
sim_smc_pref_0 <- redist::redist_smc(pref_map_0,
                                     nsims = nsims,
                                     pop_temper = 0.05)
```

# 2.6 Save results of simulation
```{r}
saveRDS(sim_smc_pref_0, paste("simulation/",
                              as.character(pref_code),
                              "_",
                              as.character(pref_name),
                              "_",
                              as.character(sim_type),
                              "_",
                              as.character(nsims),
                              "_0",
                              ".Rds",
                              sep = ""))
```


# 3. Run Simulations with 1 Municipality Split
