---
title: "Standard Process for Rural Prefectures: Fukushima Prefecture as an Example"
output: html_document:
  toc: true
  toc_float: true 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '/Users/reiyatsuhashi/Documents/GitHub/japan')
#knitr::opts_knit$set(root.dir = '/home/kentoyamada/R/jcdf/')
```

# I. Simulations
## 1. Set Up and Data Cleaning Process
### 1.1 Set Up
```{r eval=FALSE, warning = FALSE, message = FALSE}
library(tidyverse)
set.seed(12345)

# pull functions from jcdf
# set working directory to the function folder
setwd("R")
files.sources = list.files()
sapply(files.sources, source)
# set working directory back to `jcdf`
setwd("..")
```

#### Define Prefectural Data 
```{r}
sim_type <- "smc"
nsims <- 25000
pref_code <- 07
pref_name <- "fukushima"
lakes_removed <- c() 
ndists_new <- 4
ndists_old <- 5
```


### 1.2.Download and Clean Census Data
```{r warning=FALSE, message=FALSE}
# download census shapefile
pref_raw <- download_shp(pref_code)
dem_pops <- download_pop_demographics(pref_code)

# download 2020 census data
total <- download_2020_census(type = "total")
foreigner <- download_2020_census(type = "foreigner")
#Clean 2020 census
census2020 <- clean_2020_census(total = total, foreigner = foreigner)

# download historical boundary data
old_boundary <- download_old_shp(pref_code = pref_code)

# populations based on historical boundaries
pop_by_old_boundary <- download_2015pop_old(pref_code = pref_code)
```

### 1.3 Use `clean_jcdf()` function to clean census data
```{r warning=FALSE, message=FALSE}
pref <- pref_raw %>%
  clean_jcdf() %>%
  dplyr::group_by(code, CITY_NAME) %>%
  dplyr::summarise(geometry = sf::st_union(geometry)) %>%
  dplyr::left_join(census2020, by = c('code')) %>%
  dplyr::rename(pop = pop_national) %>%
  dplyr::select(code, pop, geometry)
```

#### For Miyagi Prefecture only: reflect changes in municipality code
Tomiya-cho became Tomiya-shi in 2016. As we are dealing with census data both from 2015 and 2020, we must fix the municipality code of Tomiya-cho.
```{r}
# fix 富谷町 --> 富谷市 (2016 changes)
# pref[which(pref$code == 4423), ]$pop <-  (census2020 %>% dplyr::filter(code == 4216, ))$pop_national
# pref[which(pref$code == 4423), ]$code <- 4216
```

### 1.4 Use `merge_gun()` to make a new column for codes of guns
`merge_gun()` assigns each gun a unique code.
```{r}
pref <- merge_gun(pref)
```

### 1.5 Define "Koiki-renkei" Areas
```{r}
kooriyama_koiki <- c(7203, 7207, 7210, 7211, 7214, 7322, 7342, 7344, 7408, 7501, 7502, 7503, 7504, 7505, 7521, 7522)
shirakawa_koiki <- c(7205, 7461, 7464, 7465, 7466, 7481, 7482, 7483, 7484)
kitakata_koiki <- c(7208, 7402, 7405)
minamisoma_koiki <- c(7212, 7564)
yamizo_koiki <- c(7481, 7482, 7483)

pref$koiki_code <- pref$code

#filter out the municipalities that belong to this koiki_renkei area and assign new codes
koiki_1 <- pref %>% filter(code %in% kooriyama_koiki)
koiki_1$koiki_code <- rep(1, times = length((pref %>% filter(code %in% kooriyama_koiki))$koiki_code))
koiki_2 <- pref %>% filter(code %in% shirakawa_koiki)
koiki_2$koiki_code <- rep(2, times = length((pref %>% filter(code %in% shirakawa_koiki))$koiki_code))
koiki_3 <- pref %>% filter(code %in% kitakata_koiki)
koiki_3$koiki_code <- rep(3, times = length((pref %>% filter(code %in% kitakata_koiki))$koiki_code))
koiki_4 <- pref %>% filter(code %in% minamisoma_koiki)
koiki_4$koiki_code <- rep(4, times = length((pref %>% filter(code %in% minamisoma_koiki))$koiki_code))
koiki_5 <- pref %>% filter(code %in% yamizo_koiki)
koiki_5$koiki_code <- rep(5, times = length((pref %>% filter(code %in% yamizo_koiki))$koiki_code))

#bind together with the remainder
remainder <- pref %>% filter(code %in% c(kooriyama_koiki, shirakawa_koiki, kitakata_koiki, minamisoma_koiki, yamizo_koiki) == FALSE)
pref <- dplyr::bind_rows(koiki_1, koiki_2, koiki_3, koiki_4, koiki_5, remainder)
```


## 2. Run Simulations with 0 Municipality Splits (without taking into accoun "Koiki-renkei")
### 2.1 Finalize pref object
We merge together the gun and treat them as one geographical unit, except for the guns that are split under the status quo. For Fukushima, Nishishirakawa-gun (gun_code:7460) is split under the status quo, so we will allow this gun to be split.
```{r}
pref_0 <- sf::st_as_sf(
  dplyr::bind_rows(
  #Miyagi-gun
  pref %>% filter(gun_code == 7460),
  
  #Rest of prefecture: 
  pref %>%
    dplyr::filter(gun_code %in% c(7460) == FALSE) %>%
    dplyr::group_by(gun_code) %>%
    dplyr::summarize(geometry = sf::st_union(geometry),
                     pop = sum(pop),
                     code = code[1],
                     koiki_code = koiki_code[1])
  )
)
```

### 2.2 Make adjacency graph
```{r}
prefadj_0 <- redist::redist.adjacency(pref_0)
```

### 2.3 Add edges to adjacency graph
In this case, there are no edges to add as there are no areas disconnected from the mainland.
```{r}
if(check_ferries(pref_code) == TRUE){
  # add ferries
  ferries_0 <- add_ferries(pref_0)
  prefadj_0 <- geomander::add_edge(prefadj_0,
                                 ferries_0[, 1],
                                 ferries_0[, 2],
                                 zero = TRUE)
  # check contiguity
  suggest_0 <-  geomander::suggest_component_connection(shp = pref_0,
                                                      adj = prefadj_0)
  prefadj_0 <- geomander::add_edge(prefadj_0,
                                 suggest_0$x,
                                 suggest_0$y,
                                 zero = TRUE)
}
```

### 2.4 Define redist.map object
```{r}
pref_map_0 <- redist::redist_map(pref_0,
                                 ndists = ndists_new,
                                 pop_tol= 0.08,
                                 total_pop = pop,
                                 adj = prefadj_0)
```

###2.5 Run Simulation
```{r}
sim_smc_pref_0 <- redist::redist_smc(pref_map_0,
                                     nsims = nsims,
                                     pop_temper = 0.05)
```

### 2.6 Save results of simulation
```{r}
saveRDS(sim_smc_pref_0, paste("simulation/",
                              as.character(pref_code),
                              "_",
                              as.character(pref_name),
                              "_",
                              as.character(sim_type),
                              "_",
                              as.character(nsims),
                              "_0",
                              ".Rds",
                              sep = ""))
```

# II. Analysis
## 1. Get Optimal Plan
### 1.1 Extract Plans
```{r}
index_0 <- vector(length = nrow(pref))
for (i in 1:nrow(pref))
{
  if (pref$code[i] %in% pref_0$code)
  {
    index_0[i] = which(pref_0$code == pref$code[i])[1]
  }
  else
  {
    index_0[i] = which(pref_0$gun_code == pref$gun_code[i])[1]
  }
}
pref_smc_plans_0 <- redist::get_plans_matrix(sim_smc_pref_0)
pref_smc_indexed_0 <- pref_smc_plans_0[index_0, ]
prefadj <- redist::redist.adjacency(pref)
```

### 1.2 Calculate Max:min ratio
```{r, warning = FALSE}
wgt_smc_0 <- simulation_weight_disparity_table(sim_smc_pref_0)
```

```{r}
orig_adj_0 <- redist::redist.adjacency(pref_0)
```

### 1.3 Count municipality/gun/koiki renkei splits
Whereas `count_splits()` counts the total number of splits, `redist.splits()` counts the number of geographical units that are split.
```{r}
num_gun_split_0 <- count_splits(pref_smc_plans_0, pref_map_0$gun_code)
gun_split_0 <- redist::redist.splits(pref_smc_plans_0, pref_map_0$gun_code)

num_koiki_split_0 <- count_splits(pref_smc_plans_0, pref_map_0$koiki_code)
koiki_split_0 <- redist::redist.splits(pref_smc_plans_0, pref_map_0$koiki_code)
```

### 1.4 Compile Results
The table created includes information on the max:min ratio as well as the number of municipality/gun/koiki-renkei splits. We also check whether there are cases where a municipality is split into more than 2 districts, in which case such results are filtered out.

```{r}
results_0 <- data.frame(matrix(ncol = 0, nrow = nrow(wgt_smc_0)))
results_0$max_to_min <- wgt_smc_0$max_to_min

#number of gun splits
results_0$num_gun_split <- num_gun_split_0
results_0$gun_split <- gun_split_0

#number of koiki renkei area splits
results_0$num_koiki_split <- num_koiki_split_0
results_0$koiki_split <- koiki_split_0

results_0$index <- 1:nrow(wgt_smc_0)
results_0$contiguous <- 0
for (i in 1:nrow(wgt_smc_0))
{
  results_0$contiguous[i] <- max(geomander::check_contiguity(prefadj, pref_smc_indexed_0[, i])$component) == 1
}
```

### 1.5  Optimal Plan
```{r}
contiguous_results_0 <- results_0[which(results_0$contiguous == 1), ]
rownames(contiguous_results_0) <- 1:nrow(contiguous_results_0)

optimal_0 <- contiguous_results_0$index[which(contiguous_results_0$max_to_min == min(contiguous_results_0$max_to_min))][1]
```

# 2. Visualize Optimal Plan
## 2.1 0 splits
```{r}
#get data on optimal plan
matrix_optimal_0 <- redist::get_plans_matrix(sim_smc_pref_0 %>% filter(draw == optimal_0))
colnames(matrix_optimal_0) <- "district"
optimal_boundary_0 <- cbind(pref_map_0, as_tibble(matrix_optimal_0))

#get data on gun boundary
gun_boundary <- pref_0 %>%
  filter(gun_code >= (pref_map_0$code[1]%/%1000)* 1000 + 300) %>%
  group_by(gun_code) %>%
  summarise(geometry = sf::st_union(geometry))

#get data on koiki boundary
koiki_boundary <- pref_0 %>%
  filter(koiki_code < 10) %>%
  group_by(koiki_code) %>%
  summarise(geometry = sf::st_union(geometry))

#map with district data + municipality/gun/koiki-renkei boundary
ggplot() +
  geom_sf(data = optimal_boundary_0, aes(fill = factor(district))) +
  scale_fill_manual(values = c("orange", "green", "blue", "yellow", "brown")) +
  geom_sf(data = gun_boundary, fill = NA, color = "black", lwd = 1.0) +
  geom_sf(data = koiki_boundary, fill = "plum1", alpha = 0.5, color = "plum1", lwd = 0.2) +
  theme(axis.line = element_blank(), axis.text = element_blank(),
        axis.ticks = element_blank(), axis.title = element_blank(),
        legend.title = element_blank(), legend.position = "None",
        panel.background = element_blank())
```

# 3. Co-occurrence
## 3.1 Filter Out Plan with Low Max:min Ratio (Top 10%)
```{r}
good_num_0 <-  contiguous_results_0 %>%
  arrange(max_to_min) %>%
  slice(1: as.numeric(nrow(contiguous_results_0)*0.1)) %>%
  select(index)
good_num_0 <- as.vector(t(good_num_0))
sim_smc_pref_0_good <- sim_smc_pref_0 %>%
  filter(draw %in% good_num_0)
```

## 3.2 Obtain co-occurrence matrix
```{r}
m_co_0 = redist::prec_cooccurrence(sim_smc_pref_0_good, sampled_only=TRUE)
```


## 3.3 Use `cluster::agnes()` to create clusters
```{r}
cl_co_0 = cluster::agnes(m_co_0)
plot(as.dendrogram(cl_co_0)) 
prec_clusters_0 = cutree(cl_co_0, 4) #4: number of clusters
```

## 3.4 Convert data on membership to tibble
```{r}
pref_membership_0 <- as_tibble(as.data.frame(prec_clusters_0))
names(pref_membership_0) <- "membership"
```


## 3.5 Obtain co-occurrence ratio
```{r}
cooc_ratio <- vector(length = length(pref_0$code))
#----define relcomp function--------
relcomp <- function(a, b) {
  comp <- vector()
  for (i in a) {
    if (i %in% a && !(i %in% b)) {
      comp <- append(comp, i)
    }
  }
  return(comp)
}

for (i in 1:length(pref_0$code))
{
  cooc_ratio[i] <- 1 -
    sum(pref_0$pop[relcomp(prefadj_0[[i]]+1,
                              which(prec_clusters_0 == prec_clusters_0[i]))] * m_co_0[i, relcomp(prefadj_0[[i]]+1,
                                                                                                 which(prec_clusters_0 == prec_clusters_0[i]))])/
    sum(pref_0$pop[prefadj_0[[i]]+1] * m_co_0[i, prefadj_0[[i]]+1])
}

```


##3.6 Match membership data with map object
```{r}
pref_0_membership <- cbind(pref_0, cooc_ratio, pref_membership_0)

#sort membership data by group
pref_0_membership_1 <- pref_0_membership %>% dplyr::filter(membership == 1)
pref_0_membership_2 <- pref_0_membership %>% dplyr::filter(membership == 2)
pref_0_membership_3 <- pref_0_membership %>% dplyr::filter(membership == 3)
pref_0_membership_4 <- pref_0_membership %>% dplyr::filter(membership == 4)
```

##3.7 Plot
```{r}
ggplot() +
  geom_sf(data = pref_0_membership_1, aes(fill = cooc_ratio), show.legend = FALSE) +
  scale_fill_gradient(low="palegreen", high="green") +

  ggnewscale::new_scale_fill() +
  geom_sf(data = pref_0_membership_2, aes(fill = cooc_ratio), show.legend = FALSE) +
  scale_fill_gradient(low = "lightsalmon", high = "orange") +

  ggnewscale::new_scale_fill() +
  geom_sf(data = pref_0_membership_3, aes(fill = cooc_ratio), show.legend = FALSE) +
  scale_fill_gradient(low = "skyblue", high = "blue") +

  ggnewscale::new_scale_fill() +
  geom_sf(data = pref_0_membership_4, aes(fill = cooc_ratio), show.legend = FALSE) +
  scale_fill_gradient(low="yellow", high="yellow3") +

  labs(color = "Co-occurrence",
       title = "Co-occurrence Analysis: Plans with Top 10% Max-min Ratio") +
  
  geom_sf(data = gun_boundary, fill = NA, color = "black", lwd = 1.0) +

  theme(legend.box = "vertical",
        legend.title = element_text(color = "black", size = 7),
        axis.line = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        panel.background = element_blank())
```

```{r}
current_plan <- status_quo_match(pref_0)
```

```{r}
current <- data.frame(matrix(ncol = 0, nrow = 1))
current$max_to_min <- simulation_weight_disparity_table(redist::redist_plans(current_plan$ku, pref_map_0, algorithm = "smc"))$max_to_min

#number of gun splits
current$num_gun_split <- count_splits(as.matrix(current_plan$ku), pref_map_0$gun_code)
current$gun_split <- redist::redist.splits(as.matrix(current_plan$ku), pref_map_0$gun_code)

#number of koiki renkei area splits
current$num_koiki_split <- count_splits(as.matrix(current_plan$ku), pref_map_0$koiki_code)
current$koiki_split <- redist::redist.splits(as.matrix(current_plan$ku), pref_map_0$koiki_code)
```

```{r}
better_by_all <- contiguous_results_0[which(contiguous_results_0$num_gun_split <= current$num_gun_split && contiguous_results_0$gun_split <= current$gun_split && contiguous_results_0$num_koiki_split <= current$num_koiki_split && contiguous_results_0$koiki_split <= current$koiki_split), ]
best_by_all <- better_by_all$index[which(better_by_all$max_to_min == min(better_by_all$max_to_min))][1]

matrix_best_0 <- redist::get_plans_matrix(sim_smc_pref_0 %>% filter(draw == best_by_all))
colnames(matrix_best_0) <- "district"
best_boundary_0 <- cbind(pref_map_0, as_tibble(matrix_best_0))

#map with district data + municipality/gun/koiki-renkei boundary
ggplot() +
  geom_sf(data = best_boundary_0, aes(fill = factor(district))) +
  scale_fill_manual(values = c("orange", "green", "blue", "yellow", "brown")) +
  geom_sf(data = gun_boundary, fill = NA, color = "black", lwd = 1.0) +
  geom_sf(data = koiki_boundary, fill = "plum1", alpha = 0.5, color = "plum1", lwd = 0.2) +
  theme(axis.line = element_blank(), axis.text = element_blank(),
        axis.ticks = element_blank(), axis.title = element_blank(),
        legend.title = element_blank(), legend.position = "None",
        panel.background = element_blank())
```
```{r}
rbind(current, results_0[best_by_all, c(1:5)])
```
