---
title: "23_ms_aichi"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_knit$set(root.dir = '/Users/kentoyamada/Desktop/ALARM Project/jcdf')
#knitr::opts_knit$set(root.dir = '/home/kentoyamada/R/jcdf/')
```

# I. Simulations
## 1. Set Up and Data Cleaning Process
### 1.1 Set Up
```{r eval=FALSE}
library(tidyverse)
set.seed(12345)
# pull functions from jcdf
# set working directory to the function folder
setwd("R")
files.sources = list.files()
sapply(files.sources, source)
# set working directory back to `jcdf`
setwd("..")
```

#### Define Prefectural Data 
```{r}
sim_type <- "smc"
nsims <- 25000
pref_code <- 23
pref_name <- "aichi"
lakes_removed <- c() 
ndists_new <- 16
ndists_old <- 15
n_split <- 3
```

### 1.2.Download and Clean Census Data
```{r warning=FALSE, message=FALSE}
# download census shapefile
pref_raw <- download_shp(pref_code)
dem_pops <- download_pop_demographics(pref_code)
# download 2020 census data
total <- download_2020_census(type = "total")
foreigner <- download_2020_census(type = "foreigner")
#Clean 2020 census
census2020 <- clean_2020_census(total = total, foreigner = foreigner)
# download historical boundary data
old_boundary <- download_old_shp(pref_code = pref_code)
# populations based on historical boundaries
pop_by_old_boundary <- download_2015pop_old(pref_code = pref_code)
```

### 1.3 Use `clean_jcdf()` function to clean census data
```{r warning=FALSE, message=FALSE}
pref <- pref_raw %>%
  clean_jcdf() %>%
  dplyr::select(code, KIHON1, JINKO, geometry)
pref <- calc_kokumin(pref, dem_pops)
#Estimate 2020 pop. <- estimate_2020_pop(pref, census2020) %>%
  dplyr::select(code, KIHON1, pop_estimate, geometry) %>%
  dplyr::rename(subcode = KIHON1, pop = pop_estimate)
```

### 1.4 Merge together gun
Under the enacted plan, all the gun in Aichi prefecture are respected under the status quo. Thus, we merge together the gun so as not to split them.
```{r}
#merge Aichi gun
aichi <- pref %>%
  dplyr::filter(code == 23302)
aichi$code <- 23300
aichi <- aichi %>%
  dplyr::group_by(code) %>%
  dplyr::summarise(pop = sum(pop), geometry = sf::st_union(geometry))
aichi$subcode <- "0000"

#merge Nishikasugai gun
nishikasugai <- pref %>%
  dplyr::filter(code == 23342)
nishikasugai$code <- 23340
nishikasugai <- nishikasugai %>%
  dplyr::group_by(code) %>%
  dplyr::summarise(pop = sum(pop), geometry = sf::st_union(geometry))
nishikasugai$subcode <- "0000"

#merge Niwa gun
niwa <- pref %>%
  dplyr::filter(code %in% c(23361, 23362))
niwa$code <- 23360
niwa <- niwa %>%
  dplyr::group_by(code) %>%
  dplyr::summarise(pop = sum(pop), geometry = sf::st_union(geometry))
niwa$subcode <- "0000"

#merge Ama gun
ama <- pref %>%
  dplyr::filter(code %in% c(23424, 23425, 23427))
ama$code <- 23420
ama <- ama %>%
  dplyr::group_by(code) %>%
  dplyr::summarise(pop = sum(pop), geometry = sf::st_union(geometry))
ama$subcode <- "0000"

#merge Chita gun
chita <- pref %>%
  dplyr::filter(code %in% c(23441, 23442, 23445, 23446, 23447))
chita$code <- 23440
chita <- chita %>%
  dplyr::group_by(code) %>%
  dplyr::summarise(pop = sum(pop), geometry = sf::st_union(geometry))
chita$subcode <- "0000"

#merge Nukata gun
nukata <- pref %>%
  dplyr::filter(code == 23501)
nukata$code <- 23500
nukata <- nukata %>%
  dplyr::group_by(code) %>%
  dplyr::summarise(pop = sum(pop), geometry = sf::st_union(geometry))
nukata$subcode <- "0000"

#merge Kitashitara gun
kitashitara <- pref %>%
  dplyr::filter(code %in% c(23561, 23562, 23563))
kitashitara$code <- 23560
kitashitara <- kitashitara %>%
  dplyr::group_by(code) %>%
  dplyr::summarise(pop = sum(pop), geometry = sf::st_union(geometry))
kitashitara$subcode <- "0000"

#merge back together
pref_non_gun <- pref %>%
  dplyr::filter(code %in% c(23302, 
                           23342,
                           23361, 23362,
                           23424, 23425, 23427,
                           23441, 23442, 23445, 23446, 23447,
                           23501,
                           23561, 23562, 23563) == FALSE)

#now pref is an object with 0 gun splits
pref <- dplyr::bind_rows(pref_non_gun, aichi, nishikasugai, niwa, ama, chita, 
                         nukata, kitashitara)
```

### 1.5 Define "Koiki-renkei" Areas
```{r}
#assign which municipality belongs to which koiki renkei area
kinuura_koiki <- c(23210, 23225, 23227, 23300)  #23300 Aichigun, Togo cho
```

## 2. Run Simulations 

### 2.1 Finalize pref object
No additional steps needed

### 2.2 Make adjacency graph
```{r}
prefadj <- redist::redist.adjacency(pref)
```

### 2.3 Add edges to adjacency graph
The add_ferries() function connects 西尾市一色町佐久島 (no: 4251, code: 23213, subcode: 7240) with 西尾市一色町坂田新田 (no: 4239, code: 23213, subcode: 7120).

In addition, 名古屋市港区金城ふ頭 (no: 973, code: 23111, subcode: 0460) appears to be disconnected. We manually connect it to three areas: 名古屋市港区空見町(code: 23111, subcode: 1080), 名古屋市港区潮見町 (code: 23111, subcode: 0740), and 愛知県海部郡飛島村金岡(code: 23420)

We also manually connect 常滑市セントレア町(no: 4403, code: 23216, subcode: 0960) to 常滑市りんくう町 (code: code: 23216, subcode: 0950)
```{r}
if(check_ferries(pref_code) == TRUE){
  # add ferries
  ferries <- add_ferries(pref)
  prefadj <- geomander::add_edge(prefadj,
                                 ferries[, 1],
                                 ferries[, 2],
                                 zero = TRUE)
}
```

```{r}
prefadj <- geomander::add_edge(prefadj, 
                               which(pref$code == 23111 & pref$subcode == "0460"), #名古屋市港区金城ふ頭 
                               which(pref$code == 23111 & pref$subcode == "1080")) #名古屋市港区空見町
prefadj <- geomander::add_edge(prefadj, 
                               which(pref$code == 23111 & pref$subcode == "0460"), #名古屋市港区金城ふ頭 
                               which(pref$code == 23111 & pref$subcode == "0740")) #名古屋市港区潮見町
prefadj <- geomander::add_edge(prefadj, 
                               which(pref$code == 23111 & pref$subcode == "0460"),  #名古屋市港区金城ふ頭 
                               which(pref$code == 23420)) #愛知県海部郡飛島村金岡
prefadj <- geomander::add_edge(prefadj, 
                               which(pref$code == 23216 & pref$subcode == "0960"), #常滑市セントレア町 
                               which(pref$code == 23216 & pref$subcode == "0950")) #常滑市りんくう町
```


### 2.4 Define redist.map object
```{r}
pref_map <- redist::redist_map(pref,
                               ndists = ndists_new,
                               pop_tol= 0.15,
                               total_pop = pop,
                               adj = prefadj)
```

###2.5 Run Simulation
```{r}
#define constraints
constr = redist::redist_constr(pref_map)
constr = redist::add_constr_splits(constr, strength=2)
constr = redist::add_constr_multisplits(constr, strength = 10)

#run redist_smc
pref_smc <- redist::redist_smc(
  map = pref_map,
  nsims = 10,
  counties = pref$code,
  constraints = constr
)
```

### 2.6 Save results of simulation
```{r}
saveRDS(pref_smc, paste("simulation/",
                        as.character(pref_code),
                        "_",
                        as.character(pref_name),
                        "_",
                        as.character(sim_type),
                        "_",
                        as.character(nsims),
                        "_0",
                        ".Rds",
                        sep = ""))
```


